%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Gefei Zuo}{
	\textsmaller{
		Downloadable at \href{https://github.com/Alkaid-Benetnash/CV}{https://github.com/Alkaid-Benetnash/CV}
	}
}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent Email: \href{mailto:zgf574564920@gmail.com}{\mbox{zgf574564920@gmail.com}}, Phone: \textsmaller{+}86.15656577795
\\
Address: Room 212, Building 321, USTC, No.96, JinZhai Road, Hefei, Anhui, China.
\\
\noindent 4th year undergraduate student

\spacedhrule{0.2em}{-1em}  % a horizontal line with some vertical spacing before and after

\roottitle{Education}

\headedsection  % sets the header for the section and includes any subsections
{\href{http://ustc.edu.cn}{University of Science and Technology of China}}
{\textsc{Hefei, Anhui, China}} {%
	\headedsubsection
	{B.S. in Computer Science (School of Gifted Young)}
	{Sept.\apo2014 -- present}
	{\bodytext {
			\begin{itemize}
				\item GPA 3.75/4.30, Rank 15/140
				\item Enrolled in the Talent Program in Computer and Information Science and Technology
			\end{itemize}
	}}
}


\spacedhrule{0.2em}{-1em}

\roottitle{Research Experience}
\headedsection
{System Group Intern, instructed by \href{https://www.microsoft.com/en-us/research/people/lintaoz/}{Lintao Zhang}}
{\textsc{Microsoft Research Asia}}
{
	\headedsubsection
	{Efficient and Scalable Total-Order Message Scattering in Datacenter Network[\ref{pub:toms}]}
	{Jul.\apo 2017 -- Oct.\apo 2017}
	{\bodytext{
			\begin{itemize}
				\item Offload reordering and buffering to endhost: separate control plane from data plane.
				\item Readily deployable: programmable switches, commodity switches, endhosts only.
				\item Accelerate distributed transactional processing by 10X with litter overhead.
			\end{itemize}
	}}
}
\headedsection
{Soft Robot Lab, instructed by \href{http://ai.ustc.edu.cn/}{Xiaoping Chen}}
{\textsc{Univ. of Science and Tech. of China}}
{
	\headedsubsection
	{Whole manipulator control in constrained environments[\ref{pub:softrobot}]}
	{Dec.\apo 2016 -- Mar.\apo 2017}
	{\bodytext{
			\begin{itemize}
				\item Extend traditional Jacobians method with new constraints, take obstacle's information into account.
				\item Enable our softrobot work in environments with obstacles.
			\end{itemize}
	}}
}

\spacedhrule{0.2em}{-1em}
\roottitle{Publications}
\publication
	{Efficient and Scalable Total-Order Message Scattering in Datacenter Network\label{pub:toms}}
	{Bojie Li, \textbf{Gefei Zuo}, Wei Bai, Enhong Chen, Lintao Zhang}
	{Submitted to EuroSys'18}
\publication
	{Whole manipulator control in constrained environments\label{pub:softrobot}}
	{Dengyuan Wang, Xiaotong Chen, \textbf{Gefei Zuo}, Xinghua Liu, Zhanchi Wang, Hao Jiang and Xiaoping Chen}
	{Submitted to ICRA'18}
\spacedhrule{0.5em}{-1em}

\roottitle{Work Experience}

\headedsection  % sets the header for the section and includes any subsections
{USTC Freeshell}
{\textsc{Univ. of Science and Tech. of China}} {
	\headedsubsection
	{Maintainer}
	{Sept.\apo 2014 -- Jul.\apo 2017}
	{\bodytext{
			\begin{itemize}
				\item An IaaS service for students to learn and use Linux, supporting various Linux distributions.
				\item Utilize OS level virtualization (OpenVZ), distributed storage (Ceph), dynamic routing (RIP).
			\end{itemize}
		}}
	}

\headedsection  % sets the header for the section and includes any subsections
{\href{https://mirrors.ustc.edu.cn}{USTC OpenSource Mirrors}}
{\textsc{Univ. of Science and Tech. of China}} {%
	\headedsubsection
	{Maintainer}
	{Jul.\apo 2015 -- Mar.\apo 2017}
	{\bodytext{
			\begin{itemize}
				\item It is one of the biggest OpenSource mirror in China, hosts 25TiB+ content, has 10TiB+ traffic per day.
%				\item Test and deploy several kinds of block cache, finally improve the disk IO capability more than twice
				\item Deal with many kinds of performance or software/hardware issues.
			\end{itemize}
		}}
	}

\headedsection  % sets the header for the section and includes any subsections
{\href{https://github.com/zzh1996/distributed-file-storage}{Distributed File Storage}}
{\textsc{Univ. of Science and Tech. of China}} {%
	\headedsubsection
	{Team project of Principles and Design of Operating Systems}
	{Mar.\apo 2016 -- Jun.\apo 2016}
	{\bodytext{
			\begin{itemize}
				\item Implement git-like(content hash as index) file/directory indexing API for web frontend.
				\item Design and Implement synchronize operation based on concept of blockchain.
			\end{itemize}
	}}
}

\headedsection
{Pipeline MIPS CPU on FPGA}
{\textsc{Univ. of Science and Tech. of China}} {%
	\headedsubsection
	{Course project of Computer Organization}
	{May.\apo2016}
	{\bodytext{
			\begin{itemize}
				\item Implemented in Verilog, 5 stage pipeline, 40 instructions, exception support.
			\end{itemize}
	}}
}

\spacedhrule{0em}{-1em}

\roottitle{Awards}
\timedentry{SOSP'17 Student Research Competition (Undergraduate Category) silver medal}{Oct.\apo2017}
\timedentry{USTC Outstanding Student Scholarship (Grade 2)}{2016, 2017}

\spacedhrule{0.2em}{-1em}

\roottitle{Extracurricular Activities}

\timedentry{President, Linux User Group, USTC}{May.\apo2016 -- June.\apo2017}
\timedentry{Vice President, Linux User Group, USTC}{May.\apo2015 -- May.\apo2016}
\timedentry{Vice Minister, Technology team, Student Union, Special Class of the Gifted Young}{Sept.\apo2015 -- May.\apo2016}

\spacedhrule{0.2em}{-1em}

\roottitle{Skills}
\timedentry{\textbf{Programming:} C/C++, Python, Matlab, Bash, Verilog
}{}
\timedentry{\textbf{Linux:} Network management, Server maintenance}{}
\timedentry{\textbf{Github:} \href{https://github.com/Alkaid-Benetnash}{https://github.com/Alkaid-Benetnash}
}{}
%\inlineheadsection{Programming:}{C/C++, Python, Matlab, Bash, Verilog}
%\inlineheadsection{Linux:}{Network management, Server maintaining}
%\inlineheadsection{Github:}{\href{https://github.com/Alkaid-Benetnash}{https://github.com/Alkaid-Benetnash}}

\end{document}
